PANCHANGE_analysis

### 2020-12-09 PANCHANGE_analysis.Rmd
added chunks to run plot function for all configurations

>>>>

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=14, fig.width=8}

lm.forest(plot.dat.disorder.prepan,"Predictors of pandemic symptoms controlling for prepandemic symptoms")

```{r forest plot by disorder retro, fig.height=14, fig.width=8}

lm.forest(plot.dat.disorder.retro,"Predictors of pandemic symptoms controlling for retrospective symptoms")

```
### time point 
```{r forest plot by time point gad, fig.height=14, fig.width=8}

lm.forest(plot.dat.time.gad,"Predictors of anxiety during pandemic controlling for retrospective or prepandemic symptoms")

```
```{r forest plot by time point phq, fig.height=14, fig.width=8}

lm.forest(plot.dat.time.phq,"Predictors of depression during pandemic controlling for retrospective or prepandemic symptoms")

```
```{r forest plot by time point pcl, fig.height=14, fig.width=8}

lm.forest(plot.dat.time.phq,"Predictors of PTSD during pandemic controlling for retrospective or prepandemic symptoms")

```
### Sample (retrospective only)

```{r forest plot by sample retro only gad, fig.height=14, fig.width=8}

lm.forest(plot.dat.sample.gad ,"Predictors of anxiety controlling for retrospective symptoms across samples")

```
```{r forest plot by sample retro only phq, fig.height=14, fig.width=8}

lm.forest(plot.dat.sample.phq ,"Predictors of depression controlling for retrospective symptoms across samples")

```
```{r forest plot by sample retro only pcl, fig.height=14, fig.width=8}

lm.forest(plot.dat.sample.pcl ,"Predictors of PTSD controlling for retrospective symptoms across samples")
